### 2014-04-13 stat246/hw2.tex
s2 done

\end{document}

>>>>

\subsection*{7}
Since the number of samples from each distribution is equal, the decision can be made by just seeing which of the likelihoods is greater. Doing so, we obtain the following plot of the decision boundaries, each a locus of solutions to a quadratic $x^TAx+b^Tx+c=0$. The black curve is the boundary obtained from using the true parameters, the red curve the non-pooled covariance, and the blue line is the linear boundary from the pooled covariance (still a quadratic, but $A=0$).

\includegraphics[width=0.6\textwidth]{hw2_files/boundaries.png}

The red curve from the non-pooled covariance is pretty different from the true decision boundary -- it classifies a lot of points to the side as being from the first distribution instead of the second, as the true decision boundary does. However, the linear decision boundary looks a lot more reasonable -- if we had to draw a line separating the two distributions (with assumed equal covariance), one with mean at $(0,2)$ and the other with mean at $(0,0)$, a straight line through $(0,1)$ would be the reasonable choice. Indeed, we see this in the error rates. The true decision boundary achieved an error rate of $0.0465$, the nonpooled covariance an error rate of $0.0955$, and the pooled covariance an error rate of $0.08$, so the simpler decision boundary actually acheived a better error rate.

Also notable is the fact that the equal-covariance assumption is way off in this case. The two distributions are cigar-shaped, but aligned in perpendicular directions, so with enough samples, the pooled covariance should end up with two very similar eigenvalues. Nevertheless, with so few samples, it's still possible for it to do better than a wildly inaccurate quadratic boundary.
\end{document}
